---
output: 
  github_document:
    html_preview: true
always_allow_html: true
---

# MPI : Multidimensional Poverty Index (Alkire-Foster Method)

The **mpi** package provides tools to compute the Multidimensional Poverty Index (MPI) using the Alkire-Foster methodology.

It allows users to input binary deprivation indicators, assign weights, and specify a global poverty cutoff (k). The package returns:

- A data frame with individual deprivation scores and poverty status
- A summary table with key statistics: Incidence (H), Intensity (A), and MPI
- An interactive **plotly** barplot of poverty status

## Installation

```{r}
# Install from GitHub
# remotes::install_github("julienParfait/MPI")
```

## Example 

```{r}
library(mpi)

data <- data.frame(
  edu = c(1, 0, 1, 1, 0),
  health = c(0, 1, 1, 1, 0),
  water = c(1, 0, 1, 1, 1)
)

weights <- c(0.4, 0.3, 0.3)
k <- 0.33

res <- MPI(data, weights, k)

head(res$data)
res$summary
#res$plot

```

## Visualisation 


```{r save-plot, echo=FALSE, fig.align="center", fig.cap="Distribution of Poverty Status", out.width="70%"}
library(ggplot2)
# Data
df <- data.frame(
  status = c("Non-poor", "Poor"),
  pct = c(40, 60)
)

# graph 
p <- ggplot(df, aes(x = status, y = pct, fill = status)) +
  geom_col() +
  geom_text(aes(label = paste0(pct, "%")), vjust = -0.5, size = 5) +
  scale_fill_manual(values = c("#27AE60", "#C0392B")) +
  labs(title = "Poverty Status Distribution", x = "Poverty Status", y = "Percentage") +
  theme_minimal()

if (!dir.exists("man/figures")) {
  dir.create("man/figures", recursive = TRUE)
}

ggsave("man/figures/poverty_status.png", p, width = 6, height = 4, dpi = 300)

p
```



## Output Meaning

* H (Headcount ratio): Proportion of people who are multidimensionally poor

* A (Intensity): Average share of deprivations among the poor

* MPI: The product of H and A




