---
output: 
  github_document:
    html_preview: true
always_allow_html: true
---

# mpi: Multidimensional Poverty Index (Alkire-Foster Method)

The **mpi** package provides tools to compute the Multidimensional Poverty Index (MPI) using the Alkire-Foster methodology.

It allows users to input binary deprivation indicators, assign weights, and specify a global poverty cutoff (`k`). The package returns:

- A data frame with individual deprivation scores and poverty status
- A summary table with key statistics: Incidence (H), Intensity (A), and MPI
- An interactive `plotly` barplot of poverty status

## Installation

```{r}
# Install from GitHub
# remotes::install_github("julienParfait/MPI")
```

## Example 

```{r}
library(mpi)

data <- data.frame(
  edu = c(1, 0, 1, 1, 0),
  health = c(0, 1, 1, 1, 0),
  water = c(1, 0, 1, 1, 1)
)

weights <- c(0.4, 0.3, 0.3)
k <- 0.33

res <- MPI(data, weights, k)

head(res$data)
res$summary
res$plot

```


## Output Meaning

* H (Headcount ratio): Proportion of people who are multidimensionally poor

* A (Intensity): Average share of deprivations among the poor

* MPI: The product of H and A




